The Gravettian-Solutrean transition in westernmost Iberia: new data from the sites of Vale Boi and Lapa do Picareiro

### 2020-04-22 analysis/paper/paper.Rmd
structure changed

For lithic analysis we adopted an attribute-based methodology, which aims to describe morphological and metrical attributes of technological classes. The attributes analyzed followed those present in specialized literature, such as @brezillon1968 and @tixier1980, paired with the methodologies used in Upper Paleolithic lithic attribute analysis works, such as @bicho1992, @zilhao1997 or @almeida2000.

@@

@@

## Assemblage and raw materials

>>>>

For lithic analysis we adopted an attribute-based methodology, which aims to describe morphological and metrical attributes of technological classes. The attributes analyzed followed those present in specialized literature, such as @brezillon1968 and @tixier1980, paired with apprcascalheira2010,hes used in o)ther Upper Paleolithic lithic attribute analysis (see e.g. @bicho1992, @zilhao1997, @cascalheira2010, @almeida2000).

@@

## Stratigraphy and chronology

@@

## Lithic assemblages
